How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-04-16 tse-paper/content.tex
add corrections ttv - conclusion

\begin{table*}[tbhp]
\centering
\caption{Overview of build log analysis techniques.}
\begin{tabularx}{\textwidth}{@{}lXl@{}}
\toprule
Name			     & Sources	& Frequency	  \\
\midrule
Parser	&
~{\smallish
\cite{vassallo2018un-break,zhang2016android,seo2014programmers,hassan2019tackling,hassan2017automatic,chromy2007integration,mesbah2019deepdelta,wen2018blimp,kwon2018prioritizing,adams2007design,rahman2018impact,brandyberry2006continuous,tomassi2019bugswarm,ren2018automated,vassallo2019automated,cavalcanti2019impact,sippola2013qt,felipe2012towards,shi2018evaluating,urli2018design,selberg2012use}}
&
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_21.pdf}
\\
Regular expression
&\cite{beller2017oops,hassan2017change,macho2018automatically,vassallo2017a-tale,lou2019history,hassan2017automatic,rott2019empirische,zampetti2019study,zhao2018comparing,rausch2017empirical,ghaleb2019studying,zampetti2017open,zhang2019large,kavaler2019tool,morris2010experience}
&
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_15.pdf}
\\
Manual inspection  &
\cite{sulir2016quantitative,hassan2017automatic,bouabana2019theory,barinov2017applying,silva2018build,ghaleb2019empirical,marcozzi2019systematic,hukkanen2015adopting,rausch2017empirical,hassan2017mining,zolfagharinia2017not,cassee2019impact}
&
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_12.pdf}
\\
Machine Learning  &
\cite{hassan2017change,lou2019history,lindqvist2019detection,ren2018automated,schulz2017active}
&
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_5.pdf}
\\
\makecell[cl]{{\smallish Natural Language Processing}}	&
\cite{hassan2017change,lou2019history,schulz2017active} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\
Information Retrieval  &
\cite{hassan2017change,lindqvist2019detection,ren2018automated} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\
Analysis  &
\cite{sulir2016quantitative,haghighatkhah2018test,durieux2019critical} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\
Keyword Search	&
\cite{brandyberry2006continuous,zhang2019large,kavaler2019tool} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\
Scan  & \cite{clemencic2014new,hibbard2001visualization} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_2.pdf}
\\
Other  &
\cite{zhang2016android,hassan2017change,lou2019history,silva2018build,ren2018automated,schulz2017active}
&
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_10.pdf}
\\
None identified  &
\cite{macho2017preventing,felipe2012towards,orellana2017differences,madeyski2017continuous,zhao2017impact,santolucito2018statically,makihara2018multi,mcintosh2012evolution,gallaba2018noise,matthies2016scrumlint}
&
\\
\bottomrule
\end{tabularx}
\label{tab:litsur:techniques}
\end{table*}

% TODO one source might contribute multiple times to 'other'

@@

\noindent
\textbf{Implementation}
\label{sec:prose:impl}
% TODO we need to say something about why we think that these
% limtiations do not actually harm our results
Our results depend on the implementation of the investigated chunk
retrieval techniques and the libraries we used.
Our implementation of
PBE is based on the program synthesis provided by PROSE\@.
The
idiosyncrazies of this framework influence our PBE results.
Other
frameworks similar to PROSE might have somewhat different strengths
and weaknesses.
For example, the need for examples from a single
structural category stems from the fact that PROSE cannot learn
regular expression programs with arbitrary boolean conjunctions and
disjunctions~\cite{mayer2015user}.
PROSE introduced this constraint to
keep the synthesis performance reasonable.
At the same time, this is
clearly a current theoretical challenge of all PBE implementations,
and we therefore attribute it to the technique itself, rather than the
specific implementation.

@@

\noindent
\textbf{Data Set}
The outcomes of our comparison study are highly dependent on the build
logs from the \emph{LogChunks} data set.
It only consists of build
logs from open source projects and therefore it is not clear whether
our results are generalizable to industry projects.
We only collected
build logs from Travis CI, however we chose to evaluate on an
information chunk whose format is not dependent on Travis CI\@.
This
is because the reason the build failed is described within the build
logs by the tools themselves and not the Travis CI environment.

\noindent
\textbf{Training Set Size}
Especially the results for CTS might be influenced by the fact that we
only trained on one to five examples.
We chose this small training set
size as the training examples have to be provided per repository and
we expect a developer to not want to provide more examples than the
small numbers we evaluated on.

\noindent
\textbf{Few Samples with Many Structural Categories}
Our comparison study shows fewer measurements with many structural
categories than with one category.
This stems from the fact that we investigated the chunk retrieval
techniques on a realistic data set, which showed to often have few
structural categories within one project.

@@

There are various future research opportunities based on our work:
\begin{itemize}
  \item \textbf{Systematic Survey of Industry Approaches for Build
  Log Analysis} Our survey is limited to academic work and articles.
  However, handling build logs is a challenge for a wide range of
  practitioners as well.
  We propose to investigate the methods used in industry to analyze
  build logs.
  An example is the Jenkins \emph{build-failure-analyzer}
  plugin~\cite{jenkins2020failure-analyzer} or automatically
  inferred test results in Azure~\cite{azure2020inferred}.
  \item \textbf{Further Analysis of \emph{LogChunks}} We created the
  \emph{LogChunks} data set \cite{brandt2020logchunks} specifically for
  the comparative
  study in this paper, though it can be the basis for various further
  analyses of build log data.
  The keywords, for example, can be
  investigated to answer which keywords are used to search for the
  reason the build failed within build logs.
  \item \textbf{Cross-Repository Build Log Analysis} We trained and
  tested each chunk retrieval technique on examples from the same
  repository.
  We propose to analyze how techniques could be trained
  across repositories, building the cornerstones for build
  environment-agnostic analysis tools.
  \item \textbf{Comparison with more Chunk Retrieval Techniques} This
  paper investigates the three chunk retrieval techniques PBE, CTS and
  KWS\@.
  Our study design can be reused to evaluate other build log
  analysis techniques, such as the diff and information retrieval
  approach by Amar et al.~\cite{amar2019mining}.
  \item \textbf{Refinement of Retrieval Quality for each Technique} We
  investigated basic configurations of existing techniques applied to
  chunk retrieval from build logs.
  In a next step, each of these
  techniques could be refined to better approach the domain of build
  logs.
  The \emph{LogChunks} data set and our study results act as a
  baseline to benchmark such technique improvements.
  We propose the
  following improvements:
    \begin{itemize}
      \item \textbf{Custom Ranking and Tokens for PBE} The program
      synthesis through PROSE ranks possible programs according to
      what the user most likely intended.
      One could adapt the ranking
      rules provided by the FlashExtract DSL to fit common build log
      chunk retrieval tasks.
      FlashExtract includes special tokens when
      enumerating possible regular expressions.
      One could extend these
      with tokens found in build logs, such as ``-'',``='',``ERROR''
      or ``[OK''.
      \item \textbf{Meta-Parameter Optimization for CTS} Information
      retrieval techniques have various meta-parameters which can be
      optimized for the specific use
      case~\cite{panichella2016parameterizing}.
      We propose to further
      investigate improvements in preprocessing of the log text, in
      tokenization of the log lines into terms and in stop words
      lists.
    \end{itemize}
  \item \textbf{Usability Analysis of Chunk Retrieval Output} Our
  analysis of the output produced by the chunk retrieval focuses on
  precision and recall.
We propose to investigate how useful these
  outputs are to developers through controlled experiments.
\end{itemize}

\section{Conclusion}
\label{sec:conclusion-fw}
The goal of this paper was to support researchers and developers in
their decision on how to analyze build logs.
We implemented and
compared three different chunk retrieval techniques on our data set
\emph{LogChunks}, composed of 797 manually labeled build logs from a
broad range of 80 repositories.
Our results show that the structural
representation of the targeted information in the build logs is the
main factor to consider when choosing a suitable technique.
Secondary
factors are the desired confidence into recall and precision of the
produced output and whether precision or recall is more important for
the task at hand.

>>>>

\addtolength{\tabcolsep}{-5pt}
\begin{table*}[tbhp]
\tinyish
\centering
\caption{Overview of build log analysis techniques.}
\begin{tabularx}{\textwidth}{@{}lXl@{}}
\toprule
Name			     & Sources	& Frequency	  \\
\midrule
Parser	&
\cite{vassallo2018un-break,zhang2016android,seo2014programmers,hassan2019tackling,hassan2017automatic,chromy2007integration,mesbah2019deepdelta,wen2018blimp,kwon2018prioritizing,adams2007design,rahman2018impact,brandyberry2006continuous,tomassi2019bugswarm,ren2018automated,vassallo2019automated,cavalcanti2019impact,sippola2013qt,felipe2012towards,shi2018evaluating,urli2018design,selberg2012use}
&
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_21.pdf}
\\
Regular expression
&\cite{beller2017oops,hassan2017change,macho2018automatically,vassallo2017a-tale,lou2019history,hassan2017automatic,rott2019empirische,zampetti2019study,zhao2018comparing,rausch2017empirical,ghaleb2019studying,zampetti2017open,zhang2019large,kavaler2019tool,morris2010experience}
&
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_15.pdf}
\\
Manual inspection  &
\cite{sulir2016quantitative,hassan2017automatic,bouabana2019theory,barinov2017applying,silva2018build,ghaleb2019empirical,marcozzi2019systematic,hukkanen2015adopting,rausch2017empirical,hassan2017mining,zolfagharinia2017not,cassee2019impact}
&
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_12.pdf}
\\
Machine Learning  &
\cite{hassan2017change,lou2019history,lindqvist2019detection,ren2018automated,schulz2017active}
&
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_5.pdf}
\\
\makecell[cl]{Natural Language Processing}	&
\cite{hassan2017change,lou2019history,schulz2017active} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\
Information Retrieval  &
\cite{hassan2017change,lindqvist2019detection,ren2018automated} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\
Analysis  &
\cite{sulir2016quantitative,haghighatkhah2018test,durieux2019critical} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\
Keyword Search	&
\cite{brandyberry2006continuous,zhang2019large,kavaler2019tool} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\
Scan  & \cite{clemencic2014new,hibbard2001visualization} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_2.pdf}
\\
Other  &
\cite{zhang2016android,hassan2017change,lou2019history,silva2018build,ren2018automated,schulz2017active}
&
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_10.pdf}
\\
None identified  &
\cite{macho2017preventing,felipe2012towards,orellana2017differences,madeyski2017continuous,zhao2017impact,santolucito2018statically,makihara2018multi,mcintosh2012evolution,gallaba2018noise,matthies2016scrumlint}
&
\\
\bottomrule
\end{tabularx}
\label{tab:litsur:techniques}
\end{table*}
\addtolength{\tabcolsep}{5pt}
% TODO one source might contribute multiple times to 'other'

@@

\textbf{Implementation}
% TODO we need to say something about why we think that these
% limtiations do not actually harm our results
Our results depend on the implementation of the investigated chunk
retrieval techniques and the libraries we used.
Our implementation of
PBE is based on the program synthesis provided by PROSE\@.
The
idiosyncrazies of this framework influence our PBE results.
Other
frameworks similar to PROSE might have somewhat different strengths
and weaknesses.
For example, the need for examples from a single
structural category stems from the fact that PROSE cannot learn
regular expression programs with arbitrary boolean conjunctions and
disjunctions~\cite{mayer2015user}.
PROSE introduced this constraint to
keep the synthesis performance reasonable.
At the same time, this is
clearly a current theoretical challenge of all PBE implementations,
and we therefore attribute it to the technique itself, rather than the
specific implementation.

@@

\textbf{Data Set}
The outcomes of our comparison study are highly dependent on the build
logs from the \emph{LogChunks} data set.
It consists of build
logs from open source projects and therefore it is not clear whether
our results apply to industry projects that use build tools
not popular in open source development.
However, \emph{LogChunks} covers a wide array of build tools,
we believe that our findings can be generalized.
We collected build logs from Travis CI.
Yet, the format of the log chunk we chose
for our evaluation is not dependent on Travis CI\@.
This
is because the reason the build failed is described within the build
logs by the tools themselves and not the Travis CI environment.

\textbf{Training Set Size}
Especially the results for CTS might be influenced by the fact that we
only trained on one to five examples.
We chose this small training set
size as the training examples have to be provided per repository and
we expect a developer to not want to provide more examples than the
small numbers we evaluated on.
The fact that PBE and CTS performed best with already two training
examples shows that our training set size is large enough to
compare the three techniques we presented.

\textbf{Few Samples with Many Structural Categories}
Our comparison study shows fewer measurements with many structural
categories than with one structural category category
(50.25\% one, 33.75\% two, 13.75\% more than two).
This stems from the fact that we investigated the chunk retrieval
techniques on a real-world data set, where there were mostly few
structural categories within one project.
In addition, a third of the measurements were conducted with two
structural categories present and these already showed the negative
effect of the number of structural categories on the performance
of the chunk retrieval techniques.

@@

There are various future research opportunities based on our work:
\begin{itemize}
  \item \textbf{Systematic Survey of Industry Approaches for Build
  Log Analysis} Our survey is limited to academic work and articles.
  However, handling build logs is a challenge for a wide range of
  practitioners as well.
  We propose to investigate the methods used in industry to analyze
  build logs.
  An example is the Jenkins \emph{build-failure-analyzer}
  plugin~\cite{jenkins2020failure-analyzer} or automatically
  inferred test results in Azure~\cite{azure2020inferred}.
  \item \textbf{Further Analysis of \emph{LogChunks}} We created the
  \emph{LogChunks} data set \cite{brandt2020logchunks} specifically for
  the comparative
  study in this paper, though it can be the basis for various further
  analyses of build log data.
  The keywords, for example, can be
  investigated to answer which keywords are used to search for the
  reason the build failed within build logs.
  \item \textbf{Cross-Repository Build Log Analysis} We trained and
  tested each chunk retrieval technique on examples from the same
  repository.
  We propose to analyze how techniques could be trained
  across repositories, building the cornerstones for build
  environment-agnostic analysis tools.
  \item \textbf{Comparison with more Chunk Retrieval Techniques} This
  paper investigates the three chunk retrieval techniques PBE, CTS and
  KWS\@.
  Our study design can be reused to evaluate other build log
  analysis techniques, such as the diff and information retrieval
  approach by Amar et al.~\cite{amar2019mining}.
  \item \textbf{Refinement of Retrieval Quality for each Technique} We
  investigated basic configurations of existing techniques applied to
  chunk retrieval from build logs.
  In a next step, each of these
  techniques could be refined to better approach the domain of build
  logs.
  The \emph{LogChunks} data set and our study results act as a
  baseline to benchmark such technique improvements.
  We propose the
  following improvements:
    \begin{itemize}
      \item \textbf{Custom Ranking and Tokens for PBE} The program
      synthesis through PROSE ranks possible programs according to
      what the user most likely intended.
      One could adapt the ranking
      rules provided by the FlashExtract DSL to fit common build log
      chunk retrieval tasks.
      FlashExtract includes special tokens when
      enumerating possible regular expressions.
      One could extend these
      with tokens found in build logs, such as ``-'',``='',``ERROR''
      or ``[OK''.
      \item \textbf{Meta-Parameter Optimization for CTS} Information
      retrieval techniques have various meta-parameters which can be
      optimized for the specific use
      case~\cite{panichella2016parameterizing}.
      We propose to further
      investigate improvements in preprocessing of the log text, in
      tokenization of the log lines into terms and in stop words
      lists.
    \end{itemize}
  \item \textbf{Usability Analysis of Chunk Retrieval Output} Our
  analysis of the output produced by the chunk retrieval focuses on
  precision and recall.
  The next step would be to investigate how useful these
  outputs are to developers through controlled experiments.
\end{itemize}

\section{Conclusion}
\label{sec:conclusion-fw}
The goal of this paper was to support researchers and developers in
their decision on how to analyze build logs.
We conducted a systematic mapping study to uncover the
state-of-research on build log analysis.
We implemented	three promising chunk retrieval techniques and
compared them on our data set
\emph{LogChunks}, composed of 797 manually labeled build logs from a
broad range of 80 repositories.
Our results show that the structural
representation of the targeted information in the build logs is the
main factor to consider when choosing a suitable technique.
Secondary
factors are the desired confidence into recall and precision of the
produced output and whether precision or recall is more important for
the task at hand.
